Diversity relationships for plants and frugivores

### 2024-09-05 code/L2/L2_3_TropicalAndes_divRelationships.Rmd
add code of determining model types, update plant-frugivore TD or FD plotting code to get labels centered and visible, long multi-plot code, add code for TD-FD relationships

# 1 km
# 5 km
# 10 km
# 25 km
# 50 km
# 75 km
# 100 km
```{r}
  # Extract cell values
  comparison_data_100km <- data.frame(Plant_Richness = plant_richness_grid_100km$num_species,
                               Frugivore_Richness = frugivore_richness_grid_100km$num_species)

  # Filter out rows where either plant or frugivore richness is zero
  comparison_data_filtered_100km <- comparison_data %>%
                                filter(Plant_Richness > 0 & Frugivore_Richness > 0)
```

```{r}
# Compare plant and frugivore richness
  ## Fit a linear model
  compare_richness_linear_summary_100km <- summary(lm(comparison_data_filtered_100km$Frugivore_Richness ~
                                                  comparison_data_filtered_100km$Plant_Richness))
  linear_r_squared_100km <- compare_richness_linear_summary_100km$r.squared

  ## Fit an exponential model
  compare_richness_exponential_summary_100km <- summary(lm(comparison_data_filtered_100km$Frugivore_Richness ~
                                                       log(comparison_data_filtered_100km$Plant_Richness)))
  exponential_r_squared_100km <- compare_richness_exponential_summary_100km$r.squared

  ## Create scatter plot with linear and exponential lines
  compare_richness_plot_100km <- ggplot(comparison_data_filtered_100km,
                                        aes(x = Plant_Richness, y = Frugivore_Richness)) +
  geom_point() +
  labs(title = paste("Plant Richness vs Frugivore Richness [", resolution_meters/1000, " km]", sep = ""),
       subtitle =  paste("Linear (Red) R-squared = ", round(linear_r_squared, 2), "\n",
                  "Exponential (Blue) R-squared = ", round(exponential_r_squared, 2)),
       x = "Plant Richness by cell", y = "Frugivore Richness by cell") +
  geom_smooth(method = "lm", se = FALSE, color = "red")+
  geom_smooth(method = "lm", se = FALSE, color = "blue", formula = y ~ log(x)) +
  coord_cartesian(xlim = c(0, NA), ylim = c(0, NA))
```

```{r}
# Fit the nonlinear model using nls
nls_model <- nls(Frugivore_Richness ~ b * exp(c * Plant_Richness), 
                 data = comparison_data_filtered_100km, 
                 start = list(b = 200, c = -0.00001),
                 algorithm = "port",
                 control = nls.control(maxiter = 500, minFactor = 1e-10, warnOnly = TRUE))

# Summary of the model
summary(nls_model)
```

# Compare r-squared by resolution
## Taxonomic diversity
```{r}
# create dataframe of resolutions and r-squared values 
#[ADD 1, 5,]
resolution <- c( 10, 25, 50, 75, 100)
#ADD compare_richness_r2_1km, compare_richness_r2_5km,
r_squared <- c(compare_richness_r2_10km, compare_richness_r2_25km, compare_richness_r2_50km, compare_richness_r2_75km, compare_richness_r2_100km)
r_squared_compare <- data.frame(resolution, r_squared)

compare_r2_by_res <- ggplot(r_squared_compare, aes(x=resolution, y=r_squared)) +
    geom_point()+
    labs(title = "R-squared values of plant-frugivore richness relationships by resolution",
         x = "Resolution (km)", y = "R-squared", fill = "Number of species")
print(compare_r2_by_res)
```
## Functional Diversity
```{r}

@@

>>>>

```{r}
plant_cellFDis_5km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantFDis_5km.csv"))
frugivore_cellFDis_5km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreFDis_5km.csv"))

plant_cellFDis_10km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantFDis_10km.csv"))
frugivore_cellFDis_10km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreFDis_10km.csv"))

plant_cellFDis_25km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantFDis_25km.csv"))
frugivore_cellFDis_25km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreFDis_25km.csv"))

plant_cellFDis_50km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantFDis_50km.csv"))
frugivore_cellFDis_50km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreFDis_50km.csv"))

plant_cellFDis_75km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantFDis_75km.csv"))
frugivore_cellFDis_75km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreFDis_75km.csv"))

plant_cellFDis_100km <- read.csv(file.path(data_path_L2,"TropicalAndes_plantFDis_100km.csv"))
frugivore_cellFDis_100km <- read.csv(file.path(data_path_L2,"TropicalAndes_frugivoreFDis_100km.csv"))
```

# Preliminary plots
Check the data and inspect possible relationships

```{r}
plot(plant_cellRichness_100km$num_species, frugivore_cellRichness_100km$num_species)
plot(plant_cellRichness_75km$num_species, frugivore_cellRichness_75km$num_species)
plot(plant_cellRichness_50km$num_species, frugivore_cellRichness_50km$num_species)
plot(plant_cellRichness_25km$num_species, frugivore_cellRichness_25km$num_species)
plot(plant_cellRichness_10km$num_species, frugivore_cellRichness_10km$num_species)
plot(plant_cellRichness_5km$num_species, frugivore_cellRichness_5km$num_species)
```

```{r}
plot(plant_cellFDis_100km$fdis_value, frugivore_cellFDis_100km$fdis_value)
plot(plant_cellFDis_75km$fdis_value, frugivore_cellFDis_75km$fdis_value)
plot(plant_cellFDis_50km$fdis_value, frugivore_cellFDis_50km$fdis_value)
plot(plant_cellFDis_25km$fdis_value, frugivore_cellFDis_25km$fdis_value)
plot(plant_cellFDis_10km$fdis_value, frugivore_cellFDis_10km$fdis_value)
plot(plant_cellFDis_5km$fdis_value, frugivore_cellFDis_5km$fdis_value)
```

```{r}
plot(plant_cellRichness_5km$num_species, plant_cellFDis_5km$fdis_value)
plot(plant_cellRichness_10km$num_species, plant_cellFDis_10km$fdis_value)
plot(plant_cellRichness_25km$num_species, plant_cellFDis_25km$fdis_value)
plot(plant_cellRichness_50km$num_species, plant_cellFDis_50km$fdis_value)
plot(plant_cellRichness_75km$num_species, plant_cellFDis_75km$fdis_value)
plot(plant_cellRichness_100km$num_species, plant_cellFDis_100km$fdis_value)
```

```{r}
plot(frugivore_cellRichness_5km$num_species, frugivore_cellFDis_5km$fdis_value)
plot(frugivore_cellRichness_10km$num_species, frugivore_cellFDis_10km$fdis_value)
plot(frugivore_cellRichness_25km$num_species, frugivore_cellFDis_25km$fdis_value)
plot(frugivore_cellRichness_50km$num_species, frugivore_cellFDis_50km$fdis_value)
plot(frugivore_cellRichness_75km$num_species, frugivore_cellFDis_75km$fdis_value)
plot(frugivore_cellRichness_100km$num_species, frugivore_cellFDis_100km$fdis_value)
```

```{r}
plot(plant_cellRichness_5km$num_species, frugivore_cellFDis_5km$fdis_value)
plot(plant_cellRichness_10km$num_species, frugivore_cellFDis_10km$fdis_value)
plot(plant_cellRichness_25km$num_species, frugivore_cellFDis_25km$fdis_value)
plot(plant_cellRichness_50km$num_species, frugivore_cellFDis_50km$fdis_value)
plot(plant_cellRichness_75km$num_species, frugivore_cellFDis_75km$fdis_value)
plot(plant_cellRichness_100km$num_species,frugivore_cellFDis_100km$fdis_value)
```

```{r}
plot(frugivore_cellRichness_5km$num_species, plant_cellFDis_5km$fdis_value)
plot(frugivore_cellRichness_10km$num_species, plant_cellFDis_10km$fdis_value)
plot(frugivore_cellRichness_25km$num_species, plant_cellFDis_25km$fdis_value)
plot(frugivore_cellRichness_50km$num_species, plant_cellFDis_50km$fdis_value)
plot(frugivore_cellRichness_75km$num_species, plant_cellFDis_75km$fdis_value)
plot(frugivore_cellRichness_100km$num_species, plant_cellFDis_100km$fdis_value)
```

# Compare diversity relationships between plants and frugivores
## Determine model types
### Richness
```{r}
diff_taxa_richness <- function(plant_Richness_grid, frugivore_Richness_grid, resolution_meters, z){
  # Extract cell values
  comparison_Richness <- data.frame(Plant_Richness = plant_Richness_grid$num_species,
                               Frugivore_Richness = frugivore_Richness_grid$num_species)

  # Filter out rows where either plant or frugivore richness is zero
  comparison_Richness_filtered <- comparison_Richness %>%
                                filter(Plant_Richness > 0 & Frugivore_Richness > 0)

  ## Create scatter plots
  (compare_Richness_plot <- ggtrendline(comparison_Richness_filtered$Plant_Richness,
               comparison_Richness_filtered$Frugivore_Richness, model = z, linewidth = 1, CI.level = NA, eSize = 4) +
      geom_point(aes(x = comparison_Richness_filtered$Plant_Richness,
                                           y = comparison_Richness_filtered$Frugivore_Richness)) +
      labs(title = paste("Plant Richness vs Frugivore Richness [", resolution_meters/1000, " km]", sep = ""),
       x = "Plant Richness by cell", y = "Frugivore Richness by cell"))

}

@@

```{r}
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "line2P")
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "line3P")
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "log2P")
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "exp2P")
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "exp3P")
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "power2P")
diff_taxa_richness(plant_cellRichness_100km, frugivore_cellRichness_100km, 100000, "power3P")
```

```{r}
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "line2P")
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "line3P")
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "log2P")
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "exp2P")
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "exp3P")
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "power2P")
diff_taxa_richness(plant_cellRichness_75km, frugivore_cellRichness_75km, 75000, "power3P")
```

```{r}
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "line2P")
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "line3P")
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "log2P")
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "exp2P")
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "exp3P")
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "power2P")
diff_taxa_richness(plant_cellRichness_50km, frugivore_cellRichness_50km, 50000, "power3P")
```

```{r}
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "line2P")
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "line3P")
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "log2P")
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "exp2P")
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "exp3P")
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "power2P")
diff_taxa_richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, "power3P")
```

```{r}
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "line2P")
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "line3P")
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "log2P")
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "exp2P")
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "exp3P")
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "power2P")
diff_taxa_richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, "power3P")
```

```{r}
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "line2P")
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "line3P")
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "log2P")
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "exp2P")
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "exp3P")
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "power2P")
diff_taxa_richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, "power3P")
```

### FDis
```{r}
diff_taxa_FDis <- function(plant_FDis_grid, frugivore_FDis_grid, resolution_meters, z){
  # Extract cell values
  comparison_FDis <- data.frame(Plant_FDis = plant_FDis_grid$fdis_value,
                               Frugivore_FDis = frugivore_FDis_grid$fdis_value)

  # Filter out rows where either plant or frugivore FDis is zero
  comparison_FDis_filtered <- comparison_FDis %>%
                                filter(Plant_FDis > 0 & Frugivore_FDis > 0)

  ## Create scatter plots
  (compare_diversity_plot <- ggtrendline(comparison_FDis_filtered$Plant_FDis,
               comparison_FDis_filtered$Frugivore_FDis, model = z, linewidth = 1, CI.level = NA, eSize = 4) +
      geom_point(aes(x = comparison_FDis_filtered$Plant_FDis,
                                           y = comparison_FDis_filtered$Frugivore_FDis)) +
      labs(title = paste("Plant_FDis vs Frugivore_FDis [", resolution_meters/1000, " km]", sep = ""),
       x = "Plant_FDis by cell", y = "Frugivore_FDis by cell"))

}
```

```{r}
diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "line2P")
diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "line3P")
diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "log2P")
diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "exp2P")
#diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "exp3P")
diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "power2P")
#diff_taxa_FDis(plant_cellFDis_100km, frugivore_cellFDis_100km, 100000, "power3P")
```

```{r}
diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "line2P")
diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "line3P")
diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "log2P")
diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "exp2P")
#diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "exp3P")
diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "power2P")
diff_taxa_FDis(plant_cellFDis_75km, frugivore_cellFDis_75km, 75000, "power3P")
```

```{r}
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "line2P")
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "line3P")
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "log2P")
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "exp2P")
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "exp3P")
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "power2P")
diff_taxa_FDis(plant_cellFDis_50km, frugivore_cellFDis_50km, 50000, "power3P")
```

```{r}
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "line2P")
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "line3P")
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "log2P")
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "exp2P")
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "exp3P")
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "power2P")
diff_taxa_FDis(plant_cellFDis_25km, frugivore_cellFDis_25km, 25000, "power3P")
```

```{r}
diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "line2P")
diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "line3P")
diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "log2P")
diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "exp2P")
#diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "exp3P")
diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "power2P")
diff_taxa_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, "power3P")
```

```{r}
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "line2P")
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "line3P")
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "log2P")
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "exp2P")
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "exp3P")
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "power2P")
diff_taxa_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, "power3P")
```

## Function for comparing diversity relationships plots
For comparing richness, use exp3P and line2P for line types
For comparing FDis, use line3P and line2P for line types

line colors: line2P is "red", line3P is "blue", exp3P is "purple"
```{r}
compare_Richness <- function(plant_Richness_grid, frugivore_Richness_grid, resolution_meters, custom_y1, custom_y2){
  # Extract cell values
  comparison_Richness <- data.frame(Plant_Richness = plant_Richness_grid$num_species,
                               Frugivore_Richness = frugivore_Richness_grid$num_species)

  # Filter out rows where either plant or frugivore richness is zero
  comparison_Richness_filtered <- comparison_Richness %>%
                                filter(Plant_Richness > 0 & Frugivore_Richness > 0)

  # Calculate Annotation position
  mean_x <- max(comparison_Richness_filtered$Plant_Richness) / 2
  annot_y <- max(comparison_Richness_filtered$Frugivore_Richness) + 25

  # Create scatter plots
  compare_Richness_plot_line2P <- ggtrendline(comparison_Richness_filtered$Plant_Richness,
               comparison_Richness_filtered$Frugivore_Richness, model = "line2P", linecolor = "red", linewidth = 1,
               CI.level = NA, summary = FALSE, show.eq = FALSE, show.pvalue = FALSE, rrp.x = mean_x, rrp.y = annot_y, 
               text.col = "red", eSize = 4) +
      geom_point(aes(x = comparison_Richness_filtered$Plant_Richness,
                                           y = comparison_Richness_filtered$Frugivore_Richness), alpha = 0.25, size = 1) +
      labs(title = paste("[", resolution_meters/1000, " km]", sep = ""),
           subtitle = "Fitted with a linear model",
       x = "Plant Richness by cell", y = "Frugivore Richness by cell") +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_y_continuous(expand = c(0, 0)) + 
      theme_minimal() +
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.text = element_text(color = "black"))

  compare_Richness_plot_exp3P <- ggtrendline(comparison_Richness_filtered$Plant_Richness,
               comparison_Richness_filtered$Frugivore_Richness, model = "exp3P", linecolor = "purple", linewidth = 1,
               CI.level = NA, summary = FALSE, show.eq = FALSE, show.pvalue = FALSE, rrp.x = mean_x, rrp.y = annot_y, 
               text.col = "purple", eSize = 4) +
      geom_point(aes(x = comparison_Richness_filtered$Plant_Richness,
                                           y = comparison_Richness_filtered$Frugivore_Richness), alpha = 0.25, size = 1) +
      labs(title = paste("[", resolution_meters/1000, " km]", sep = ""),
           subtitle = "Fitted with an exponential model",
       x = "Plant Richness by cell", y = "Frugivore Richness by cell") +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_y_continuous(expand = c(0, 0)) + 
      theme_minimal() +
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.text = element_text(color = "black"))

    # Summaries of models used for trendlines
  line2P_summary <- trendline_sum(comparison_Richness_filtered$Plant_Richness,
               comparison_Richness_filtered$Frugivore_Richness, model = "line2P")
  exp3P_summary <- trendline_sum(comparison_Richness_filtered$Plant_Richness,
               comparison_Richness_filtered$Frugivore_Richness, model = "exp3P")

  # Combine trendlines into one plot
  compare_Richness_plot_both <- ggtrendline(comparison_Richness_filtered$Plant_Richness,
               comparison_Richness_filtered$Frugivore_Richness, model = "exp3P", linecolor = "purple", linewidth = 1,
               CI.level = NA, summary = FALSE, show.eq = FALSE, show.pvalue = FALSE, show.Rsquare = FALSE) +
      geom_smooth(aes(x = comparison_Richness_filtered$Plant_Richness, y = comparison_Richness_filtered$Frugivore_Richness), 
              method = "lm", se = FALSE, color = "red", linetype = "solid") +
      geom_point(aes(x = comparison_Richness_filtered$Plant_Richness,
                                           y = comparison_Richness_filtered$Frugivore_Richness), alpha = 0.25, size = 1) +
      labs(title = paste("[", resolution_meters/1000, " km]", sep = ""),
       x = "Plant Richness by cell", y = "Frugivore Richness by cell") +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_y_continuous(expand = c(0, 0)) + 
      theme_minimal() +
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.text = element_text(color = "black"),
            text = element_text(size = 18)) +
      annotate("text", x = mean_x, y = custom_y1, label = paste("Linear R² =", round(line2P_summary$R.squared, 5)),
               color = "red", size = 6) +
      annotate("text", x = mean_x, y = custom_y2, label = paste("Exponential R² =", round(exp3P_summary$R.squared, 5)),
               color = "purple", size = 6)

  list(compare_Richness_plot_line2P = compare_Richness_plot_line2P,
       compare_Richness_plot_exp3P = compare_Richness_plot_exp3P,
       line2P_summary = line2P_summary,
       exp3P_summary = exp3P_summary,
       compare_Richness_plot_both = compare_Richness_plot_both)
}
```

```{r}
compare_FDis <- function(plant_FDis_grid, frugivore_FDis_grid, resolution_meters, custom_y1, custom_y2, custom_x){
  # Extract cell values
  comparison_FDis <- data.frame(Plant_FDis = plant_FDis_grid$fdis_value,
                               Frugivore_FDis = frugivore_FDis_grid$fdis_value)

  # Filter out rows where either plant or frugivore FDis is zero
  comparison_FDis_filtered <- comparison_FDis %>%
                                filter(Plant_FDis > 0 & Frugivore_FDis > 0)
  ## Create scatter plots
  compare_FDis_plot_line2P <- ggtrendline(comparison_FDis_filtered$Plant_FDis,
               comparison_FDis_filtered$Frugivore_FDis, model = "line2P", linecolor = "red", linewidth = 1,
               CI.level = NA, summary = FALSE, show.eq = FALSE, show.pvalue = FALSE, 
               text.col = "red", eSize = 4) +
      geom_point(aes(x = comparison_FDis_filtered$Plant_FDis,
                                           y = comparison_FDis_filtered$Frugivore_FDis), alpha = 0.25, size = 1) +
      labs(title = paste("Compare FDis [", resolution_meters/1000, " km]", sep = ""),
           subtitle = "Fitted with a linear model",
       x = "Plant FDis by cell", y = "Frugivore FDis by cell") +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_y_continuous(expand = c(0, 0)) + 
      theme_minimal() +
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.text = element_text(color = "black"))

  compare_FDis_plot_line3P <- ggtrendline(comparison_FDis_filtered$Plant_FDis,
               comparison_FDis_filtered$Frugivore_FDis, model = "line3P", linecolor = "blue", linewidth = 1,
               CI.level = NA, summary = FALSE, show.eq = FALSE, show.pvalue = FALSE, 
               text.col = "blue", eSize = 4) +
      geom_point(aes(x = comparison_FDis_filtered$Plant_FDis,
                                           y = comparison_FDis_filtered$Frugivore_FDis), alpha = 0.25, size = 1) +
      labs(title = paste("Compare FDis [", resolution_meters/1000, " km]", sep = ""),
           subtitle = "Fitted with a quadratic model",
       x = "Plant FDis by cell", y = "Frugivore FDis by cell") +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_y_continuous(expand = c(0, 0)) + 
      theme_minimal() +
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.text = element_text(color = "black"))

  # Summaries of models used for trendlines
  line2P_summary <- trendline_sum(comparison_FDis_filtered$Plant_FDis,
               comparison_FDis_filtered$Frugivore_FDis, model = "line2P")
  line3P_summary <- trendline_sum(comparison_FDis_filtered$Plant_FDis,
               comparison_FDis_filtered$Frugivore_FDis, model = "line3P")

  # Combine trendlines into one plot
  compare_FDis_plot_both <- ggtrendline(comparison_FDis_filtered$Plant_FDis,
               comparison_FDis_filtered$Frugivore_FDis, model = "line3P", linecolor = "blue", linewidth = 1,
               CI.level = NA, summary = FALSE, show.eq = FALSE, show.pvalue = FALSE, show.Rsquare = FALSE) +
      geom_smooth(aes(x = comparison_FDis_filtered$Plant_FDis, y = comparison_FDis_filtered$Frugivore_FDis), 
              method = "lm", se = FALSE, color = "red", linetype = "solid") +
      geom_point(aes(x = comparison_FDis_filtered$Plant_FDis,
                                           y = comparison_FDis_filtered$Frugivore_FDis), alpha = 0.25, size = 1) +
      labs(title = paste("[", resolution_meters/1000, " km]", sep = ""),
       x = "Plant FDis by cell", y = "Frugivore FDis by cell") +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_y_continuous(expand = c(0, 0)) + 
      theme_minimal() +
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(color = "black"),
            axis.ticks = element_line(color = "black"),
            axis.text = element_text(color = "black"),
            text = element_text(size = 18)) +
      annotate("text", x = custom_x, y = custom_y1, label = paste("Linear R² =", round(line2P_summary$R.squared, 5)),
               color = "red", size = 6) +
      annotate("text", x = custom_x, y = custom_y2, label = paste("Quadratic R² =", round(line3P_summary$R.squared, 5)),
               color = "blue", size = 6)

  list(compare_FDis_plot_line2P = compare_FDis_plot_line2P,
       compare_FDis_plot_line3P = compare_FDis_plot_line3P,
       line2P_summary = line2P_summary,
       line3P_summary = line3P_summary,
       compare_FDis_plot_both = compare_FDis_plot_both)
}
```

## 5 km
```{r}
compare_Richness_5km <- compare_Richness(plant_cellRichness_5km, frugivore_cellRichness_5km, 5000, 275, 255)
(compare_Richness_5km_linear <- compare_Richness_5km$compare_Richness_plot_line2P)
(compare_Richness_5km_exp <- compare_Richness_5km$compare_Richness_plot_exp3P)
(compare_Richness_5km_plots <- compare_Richness_5km$compare_Richness_plot_both)
compare_Richness_r2_5km_linear <- compare_Richness_5km$line2P_summary$R.squared
compare_Richness_r2_5km_exp <- compare_Richness_5km$exp3P_summary$R.squared
compare_Richness_slopecoefficent_5km_linear <- compare_Richness_5km$line2P_summary$parameter["a"]
compare_Richness_slopecoefficent_5km_exp <- compare_Richness_5km$exp3P_summary$parameter["b"]
```

```{r}
compare_FDis_5km <- compare_FDis(plant_cellFDis_5km, frugivore_cellFDis_5km, 5000, 0.8, 0.75, 0.15)
(compare_FDis_5km_linear <- compare_FDis_5km$compare_FDis_plot_line2P)
(compare_FDis_5km_quad <- compare_FDis_5km$compare_FDis_plot_line3P)
(compare_FDis_5km_plots <- compare_FDis_5km$compare_FDis_plot_both)
compare_FDis_r2_5km_linear <- compare_FDis_5km$line2P_summary$R.squared
compare_FDis_r2_5km_quad <- compare_FDis_5km$line3P_summary$R.squared
compare_FDis_slopecoefficent_5km_linear <- compare_FDis_5km$line2P_summary$parameter["a"]
compare_FDis_slopecoefficent_5km_quad <- compare_FDis_5km$line3P_summary$parameter["b"]
```

## 10 km
```{r}
compare_Richness_10km <- compare_Richness(plant_cellRichness_10km, frugivore_cellRichness_10km, 10000, 400, 370)
(compare_Richness_10km_linear <- compare_Richness_10km$compare_Richness_plot_line2P)
(compare_Richness_10km_exp <- compare_Richness_10km$compare_Richness_plot_exp3P)
(compare_Richness_10km_plots <- compare_Richness_10km$compare_Richness_plot_both)
compare_Richness_r2_10km_linear <- compare_Richness_10km$line2P_summary$R.squared
compare_Richness_r2_10km_exp <- compare_Richness_10km$exp3P_summary$R.squared
compare_Richness_slopecoefficent_10km_linear <- compare_Richness_10km$line2P_summary$parameter["a"]
compare_Richness_slopecoefficent_10km_exp <- compare_Richness_10km$exp3P_summary$parameter["b"]
```

```{r}
compare_FDis_10km <- compare_FDis(plant_cellFDis_10km, frugivore_cellFDis_10km, 10000, 0.8, 0.75, 0.15)
(compare_FDis_10km_linear <- compare_FDis_10km$compare_FDis_plot_line2P)
(compare_FDis_10km_quad <- compare_FDis_10km$compare_FDis_plot_line3P)
(compare_FDis_10km_plots <- compare_FDis_10km$compare_FDis_plot_both)
compare_FDis_r2_10km_linear <- compare_FDis_10km$line2P_summary$R.squared
compare_FDis_r2_10km_quad <- compare_FDis_10km$line3P_summary$R.squared
compare_FDis_slopecoefficent_10km_linear <- compare_FDis_10km$line2P_summary$parameter["a"]
compare_FDis_slopecoefficent_10km_quad <- compare_FDis_10km$line3P_summary$parameter["b"]
```

## 25 km
```{r}
compare_Richness_25km <- compare_Richness(plant_cellRichness_25km, frugivore_cellRichness_25km, 25000, 475, 440)
(compare_Richness_25km_linear <- compare_Richness_25km$compare_Richness_plot_line2P)
(compare_Richness_25km_exp <- compare_Richness_25km$compare_Richness_plot_exp3P)
(compare_Richness_25km_plots <- compare_Richness_25km$compare_Richness_plot_both)
compare_Richness_r2_25km_linear <- compare_Richness_25km$line2P_summary$R.squared
compare_Richness_r2_25km_exp <- compare_Richness_25km$exp3P_summary$R.squared
compare_Richness_slopecoefficent_25km_linear <- compare_Richness_25km$line2P_summary$parameter["a"]
compare_Richness_slopecoefficent_25km_exp <- compare_Richness_25km$exp3P_summary$parameter["b"]
```
